Theory about Normal Basis on $F(2^k)$

### 2016-12-07 dissertation/conclude.tex
dissertation v2:Appendix update 1

\section{Future Work}
In this section, we point out some research problems that deserve further study.
\subsection{Multivariate polynomial ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote 
next state. However, some verification requires the bit-level outputs to be classified to 
multiple sets. While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension to Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We make a conjecture in details:

\begin{Conjecture}
Assume we have 2 ring variables $x,y$, and an ideal $J$ composed by 2 generators:
$J = \langle f_y, v_x\rangle$. Here $f_y$ has the form $f_y = \mathcal F(x,y)$, where $\mathcal F$
is a 2-argument function, for example $f_y = y^2+(1+x)y+x$. And $v_x$ is "vanishing polynomial" about
$x$: $v_x = x^{q_1} - x$. Now we have another generator serving as "universal set"
$J_0 = \langle v_x, v_y\rangle$, $v_y = y^{q_2} - y$.
We conjecture that
$$V_K(J_0:J) = V_K(J_0)\setminus V_K(J).$$
And we believe this conjecture is scalable such that it is also valid for even more variables and generators like 
$J = \langle f_z, v_x,v_y,v_u,v_w\rangle$, $f_z =\mathcal F (z,x,y,u,w)$.
\end{Conjecture}

The following example illustrates a different operation from Example \ref{ex:SMPO}.
\begin{Example}
Recall that 
$\{s_0, s_1\}$ are state/pseudo inputs, $\{t_0,t_1\}$ are state/pseudo outputs, and there is a primary input (1-bit) 
$x$. We propose a new algorithm by modifying Algorithm \ref{alg:univa}

\begin{algorithm}[hbt]
\SetAlgoNoLine
 \KwIn{Transition polynomial $f_t = T + \mathcal F (S,x)$, 
	initial state ideal $from^0 = \langle S+\mathcal G(x), x^{q_1} - x\rangle$}

  $reached = from^0(T\setminus S)$\;
  \Repeat{$GB(new^i) == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB$(\langle f_t, from^{i-1}\rangle) \setminus \mathcal H(S)$\;
	$\overline{reached} = \langle T^{q_2}-T, x^{q_1} - x \rangle : reached$\;
	$new^i \gets $GB$(to^i + \overline{reached})$\;
  	$reached \gets $GB$( reached \cdot new^i)$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm (multivariate-generator ideals)}\label{alg:multi}
\end{algorithm}

Inputs of this algorithm are: transition polynomial, which is the result of word-level abstraction; initial 
states description ideal, contains 2 generators defining PI could be any inputs and state inputs $S$ is a specific
value. (Ex: $\langle S+1+\alpha, x^2+x\rangle$ means initial state$=\{11\}$,
$\langle S+x\cdot\alpha, x^2+x\rangle$ means initial states$=\{00,10\}$).

Transition polynomial calculation uses Tim's abstraction and bit-level variable substitution. After building
an elimination ideal, use RATO such that \emph{reverse\ topo\ order\ ckt\ variables }$> T > S > x$, the reduction
remainder has the form $T+\mathcal F(s_0,s_1,x)$. From word definition $S+s_0+s_1\alpha$ we get
$$s_0 = \alpha S^2+ (1+\alpha)S, s_1 = S^2+S$$
Do substitution, the transition polynomial of example ckt is 
$$f_T = T+S^3\cdot x+\alpha S^3+(1+\alpha)S^2\cdot x+S^2+S\cdot x+(1+\alpha)x+1$$

Assume we start from state $\{11\}$. First iteration, it will reach state $\{01\}$. Line 4 is to compose an
ideal with 2 generators from $from^0$ and transition polynomial $f_T$, compute its Gr\"obner basis. Note this ideal
has the form
\begin{equation}
I_{tran} = \left\{
             \begin{array}{c}
             T+\mathcal F(S,x) \\
             S + \mathcal G(x) \\
             v_x
             \end{array}  
        \right.
\end {equation}
$v_x$ is a polynomial containing only $x$, initially it should be vanishing polynomial $x^{q_1}-x$, with the program executing
it may be factorized.

@@

The traversal will run 3 iterations and terminate at 4th iteration. I list all intermediate 
results below:
\begin{itemize}
\item Iteration 1: $from^0 = \langle S+1+\alpha, x^2+x\rangle, to^1 = \langle T+1, x^2+x\rangle,
 reached = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$
\item Iteration 2: $from^1 = \langle S+1, x^2+x\rangle, to^2= \langle T+\alpha, x^2+x\rangle,
reached = \langle T^3+1, x^2+x\rangle$
\item Iteration 3: $from^2 = \langle S+\alpha, x^2+x\rangle, to^3 = \langle T+\alpha x, x^2+x
\rangle, reached = \langle T^3\cdot x+x, T^4+T, x^2+x\rangle$
\item Iteration 4: $from^3 = \langle S, x\rangle, to^4 = \langle T+1, x\rangle, new = \langle1\rangle$
\end{itemize}
The final reachable states are represented by ideal $\langle T^3\cdot x+x, T^4+T, x^2+x\rangle$,
which means $\{00,01,10,11\}$.
\end{Example}

\subsection{Use F-4 and ZDDs to Accelerate Polynomial Reduction}
In Chapter \ref{ch:reacha} and Chapter \ref{ch:normal}, by using RATO we transform the GB 
computation to a multivariate polynomial division. However, this division (reduction)
is still with exponential complexity at worst case. In a situation where 
a chain of OR gate exists, the size of polynomial will explode. For example, a chain of OR gates 
which can be written as Boolean function 
$$f = ((a\lor b) \lor c) \lor d$$
equals to following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice $f$ contains $2^4-1 = 15$ terms, which is exponential to number of variables.
The polynomial size explosion is a major factor affect the efficiency of polynomial division.

@@

% fig:ZDD

From Figure \ref{fig:ZDD} we find the size of the ZDD is $2\times4 -1 = 7$, which is linear to the number of variables.
The reduction process using ZDDs can be executed as in \cite{polybori:2009}. The graphical illustration 
of reduction in ZDDs is shown in Figure \ref{fig:reduce_steps}.

% fig:reduce_steps

\subsection{Interpolation extraction using GB Algorithm}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulae
\cite{pudlak:ci} \cite{mcmillan:interpolation}. Assume that Boolean
formulae are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

\begin{Definition}
(From \cite{mcmillan:interpolation}) Let $A$ and $B$ be Boolean
  formulae given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~iii)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

Given  the pair $(A, B)$ and their refutation proof, a procedure
called interpolation system constructs an interpolant in linear time
and space in the size of the proof \cite{mcmillan:interpolation}
\cite{pudlak:ci}. 
\end{Definition}

@@

CIs are used to derive abstractions to produce over-approximate image
operators in model checking \cite{mcmillan:interpolation}. Since $A
\implies P$, $P$ contains $A$ and is an {\it abstraction} of $A$. It
also has fewer variables, so checking  invariants on $P \wedge B$ is
easier. The interpolant is derived through a resolution proof of the
SAT problem. There can be many interpolants $P_i$ for a pair $(A,B)$; 
however, it is not feasible to explore a few or all of these
interpolants by means of the resolution proof.

\begin{Problem}
{\it As we wish to perform MC with abstraction using algebraic
  geometry, we introduce the algebraic geometry analog of CI
  and explore algorithms to compute them. We conjecture that the
  concept of CI should be related to elimination ideals, so our line
  of investigation will focus on \Grobner basis computations with
  elimination term orders for their computation.
}
\end{Problem}

@@

\begin{Problem}
{\it How can this algebraic interpolant $f_p$ (or in the general case,
  the set of polynomials $F_P$) be computed? As the interpolant $F_P$ 
contains only variables $X_C$ that are common to the polynomial sets
$F_A, F_B$, does this imply that the interpolants can be computed by
means of \Grobner bases with an elimination term order $X_A>X_B>X_C$
with $X_A, X_B$ eliminated from the problem? }
\end{Problem}

@@

\begin{Problem}
As there can be many interpolants for an ideal-pair $(J_A, J_B)$, we
will further resolve these questions:
\bi
\item Find the minimal interpolant: i.e. find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the un-eliminated
  variables. Consider Fig. \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei
\end{Problem}

\begin{figure}
\centering{
\includegraphics[width=3in]{newfig/project.eps}
\caption{Algebraic interpolant: Projection of varieties on common variables? }
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional blocks (including IP cores) and a raw netlist, 
technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as a alternative way to perform technology mapping, especially on word-level when 
given blocks represent word-level functions.

@@

Given a gate-level design $D$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $D$, and write out the mapped design $D'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $D$ with as many of $B_i$ such that the area
and timing is optimal.

\begin{figure}[hbt]
	\begin{center}
	\includegraphics[scale=0.3]{macro.png}
	\end{center}
	\caption{The outline and flow of mapping for macro blocks}
	\label{fig:macro}
\end{figure}

@@

This following part describes the sketch of our proposed approach base on loop invariant constraints \cite{sankaranarayanan2004non}.
First, a transition system is modeled by algebraic assertions; then \emph{ideal membership test}
is applied on the set of assertions to help abstract the loop invariant. "Template" is the concept
I borrowed from this paper to apply on my own approach.

1) {\bf Template and state constraints:} To effectively and efficiently utilize the ideal membership test technique, a heuristic to
generate $\F$ is needed. One heuristic can provide better coverage for loop invariant abstraction as well as
relatively small size is \emph{generic quadratic form}.

For example, a pair of state variables $\{x,y\}$'s generic quadratic form is
$$\F = a_0x^2+a_1x+a_2xy+a_3y+a_4y^2+a_5$$
It covers all possible terms with degree at most 2. $a_0\sim a_5$ are usually real number parameters,
a certain assignment about them can turn $\F$ into desired invariant. This parameterized constrain
polynomial covers all combinations of state variables can also be called a \emph{template}.

Finding a proper assignment is the major part of original paper and has potential to be even further explored
beyond that paper, and/or to be applied on different research field.

2) {\bf Initial state constraints:} For initial state, the constrains are explicit. A template is adopted and refined by Gr\"obner basis 
generated by original constrains, by equaling the remainder to 0 we can get constrains on
parameters from the template.

An example is Fig.\ref{fig:loopinv}. The template is generic quadratic form of $\{s,i,j,j_0\}$, which is
\begin{figure}[hbt]
	\begin{center}
	\includegraphics[scale=0.3]{../../../Pictures/Selection_006.png}
	\end{center}
	\caption{An example program of 2 Natural numbers' multiplication (Fig.1 from original paper)}
	\label{fig:loopinv}
\end{figure}
\begin{align}
\F =& a_0s^2+a_1s+a_2si+a_3sj+a_4sj_0\nonumber\\
&a_5i^2+a_6i+a_7ij+a_8ij_0+a_9j^2\nonumber\\
&a_{10}j+a_{11}jj_0+a_{12}j_0^2+a_{13}j_0+a_{14}\nonumber
\end{align}

Constrains of initial state: $s=0\land j=j_0$ can be interpreted to polynomials:
$\{s, j-j_0\}$. Check if it is Gr\"obner basis using \emph{Buchberger's algorithm}. Since
their leading terms are relatively prime, we can write Gr\"obner basis $G=\{s, j-j_0\}$. Its ideal
$J=\langle s,j-j_0\rangle$.

Compute multi-division $\F \xrightarrow{G}_+ r$, the remainder is
$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$.
Let it equal to 0, each coefficient will generate a constrain, solution to the system is candidate
assignment to generate invariant.
\begin{equation}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\nonumber
\end{equation}

3) {\bf Modeling state transitions:}
2 states get involved in a state transition. The technique requires to model the 2 states individually,
do multi-division separately to get remainder $r_1$ and $r_2$. Suppose a constrain polynomial for
this transition is $r_t$, we requires that when invariant for state 1 holds and transition $1\to 2$ stands,
invariant for state 2 should also holds, which is
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ could be any polynomial. Consider the system to be easy to solve, we keep $\lambda$
only taking value from real numbers.

Still take Fig.\ref{fig:loopinv} as example (also refer to Example 10 in original paper). State 1 is initial state we 
just characterized $\F = f(s,i,j,j_0)$, and the post state (state 2) have exactly the same form constrain:
$\F' = f(s',i',j',j_0')$. Considering transition relation, substitute $s'$ with $s+i$, replace $j'$
with $j-1$, and $i'$ for $i$, $j_0'$ for $j_0$, the template for state 2 is expression $f'$ in Example 10 from
original paper.

Do multi-division with Gr\"obner basis generated by transition relation, record its remainder $r_2$.
From equality $r_2 = \lambda r_1$, we get constrains for parameters. Solve the system using covering-problem-like
techniques (Part. \emph{Elimination by Splitting} in original paper). One branching result is:
$a_0,a_2\sim a_6, a_9\sim a_{14}$ are all zero; $a_1=a_7=-a_8$. Then reduced remainder 
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Desired invariant is 
$$s = i(j_0- j)$$
We knew the program calculates $i\times j_0$. Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Fig.\ref{fig:loopinv}.

{\bf Our proposed approach on technology mapping:}
Our approach borrows inspiration of "templates" from loop invariant paper. The difference is,
we are not using template polynomial to describe the system, instead we add some templates in the ideal
of macro blocks we want to map to simulate all possibilities.
1) {\bf System abstraction:}
The polynomial we use to test ideal membership should include all information of a circuit partition,
this requires us to abstract information from the system and write it into only 1 polynomial.
Usually this polynomial has the form like:
$$Z + f(i_1,i_2,\dots,i_n)$$
Here $Z$ is the output. When there is only one output, $Z$ will be a bit-level variable. However in most
cases we have multiple outputs, this asks us to write $Z$ as a word-level variable. $f$ is a Boolean
function about all inputs, and $i_1,i_2,\dots,i_n$ are all bit-level inputs.

\begin{figure}[hbt]
	\begin{center}
	\includegraphics[scale=0.2]{tobemapped.png}
	\end{center}
	\caption{An example gate-level netlist to be mapped}
	\label{fig:tobemapped}
\end{figure}

Fig.\ref{fig:tobemapped} shows an example circuit partition with $a1,b1,a0,b0$ as inputs and
$Z = \{z0,z1\}$ as outputs. If we use elements from Galois field $F_{2^2}$ to represent word $Z$,
we have $Z = z_0 + \alpha\cdot z_1$.

>>>>

\section{Future Work}
In this section, we point out some research problems that deserve further study.
\subsection{Multivariate polynomial ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote 
next state. However, in some situations we need to keep recording the relations between $T$ and
inputs, {\it i.e.} the reached states contain multivariate polynomials in $T,S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension to Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We make a conjecture as follows:

\begin{Conjecture}
Assume we are given 2 ring variables $x,y$, and an ideal $J$ composed by 2 generators:
$J = \langle f_y, v_x\rangle$. Here $f_y$ has the form $f_y = \mathcal F(x,y)$, where $\mathcal F$
is a 2-argument function, e.g. $f_y = y^2+(1+x)y+x$. And $v_x$ is the vanishing polynomial for variable
$x$: $v_x = x^{q_1} - x$. Now we have another generator serving as the universal set
$J_0 = \langle v_x, v_y\rangle$, $v_y = y^{q_2} - y$.
We conjecture that
$$V_K(J_0:J) = V_K(J_0)\setminus V_K(J)$$
And we believe this conjecture is scalable such that it is also valid for even more variables and generators like 
$J = \langle f_z, v_x,v_y,v_u,v_w\rangle$, $f_z =\mathcal F (z,x,y,u,w)$.
\end{Conjecture}

The following example illustrates a different operation from Example \ref{ex:SMPO}.
\begin{Example}
In Figure \ref{fig:fsm}
$\{s_0, s_1\}$ are state/pseudo inputs, $\{t_0,t_1\}$ are state/pseudo outputs, and there is a primary input (1-bit) 
$x$. We propose a new algorithm by modifying Algorithm \ref{alg:univa}:

\IncMargin{1em}
\begin{algorithm}[hbt]
\SetAlgoNoLine
\LinesNumbered
 \KwIn{Transition polynomial $f_t = T + \mathcal F (S,x)$, 
	initial state ideal $from^0 = \langle S+\mathcal G(x), x^{q_1} - x\rangle$}
 \KwOut{Reachable states}
  $reached = from^0(T\setminus S)$\;
  \Repeat{$GB(new^i) == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB$(\langle f_t, from^{i-1}\rangle) \setminus \mathcal H(S)$\;
	$\overline{reached} = \langle T^{q_2}-T, x^{q_1} - x \rangle : reached$\;
	$new^i \gets $GB$(to^i + \overline{reached})$\;
  	$reached \gets $GB$( reached \cdot new^i)$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm (multivariate-generator ideals)}\label{alg:multi}
\end{algorithm}
\DecMargin{1em}

The inputs of this algorithm includes transition polynomial (result of word-level abstraction) and initial 
states description ideal, which contains 2 generators corresponds to constraints of PI and combinational input $S$. 
For example, $\langle S+1+\alpha, x^2+x\rangle$ means initial state$=\{11\}$,
$\langle S+x\cdot\alpha, x^2+x\rangle$ means initial states$=\{00,10\}$).

Transition polynomial calculation uses the abstraction and bit-to-level conversion method from 
Chapter \ref{ch:reacha}. After Constructing
an elimination ideal, we impose RATO such that \emph{reverse\ topo\ order\ ckt\ variables }$> T > S > x$, the reduction
remainder has the form $T+\mathcal F(s_0,s_1,x)$. From word definition $S+s_0+s_1\alpha$ we get
$$s_0 = \alpha S^2+ (1+\alpha)S, s_1 = S^2+S$$
Do substitution, the transition polynomial of example ckt is 
$$f_T = T+S^3\cdot x+\alpha S^3+(1+\alpha)S^2\cdot x+S^2+S\cdot x+(1+\alpha)x+1$$

Assume we start from state $\{11\}$. In the first iteration, the reached state is $\{01\}$. Line 4 is to compose an
ideal with 2 generators from $from^0$ and transition polynomial $f_T$, compute its Gr\"obner basis. Note this ideal
has the form
\begin{equation}
I_{tran} = \left\{
             \begin{array}{c}
             T+\mathcal F(S,x) \\
             S + \mathcal G(x) \\
             v_x
             \end{array}  
        \right.
\end {equation}
$v_x$ is a polynomial containing only $q$-bit PI $x$, initially it should be vanishing polynomial $x^{q_1}-x$, 
with the program executing it may be factorized.

@@

The traversal will run 3 iterations and terminate at 4th iteration. I list all intermediate 
results below:
\begin{itemize}
\item Iteration 1: $from^0 = \langle S+1+\alpha, x^2+x\rangle, to^1 = \langle T+1, x^2+x\rangle,
 reached = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$
\item Iteration 2: $from^1 = \langle S+1, x^2+x\rangle, to^2= \langle T+\alpha, x^2+x\rangle,
reached = \langle T^3+1, x^2+x\rangle$
\item Iteration 3: $from^2 = \langle S+\alpha, x^2+x\rangle, to^3 = \langle T+\alpha x, x^2+x
\rangle, reached = \langle T^3\cdot x+x, T^4+T, x^2+x\rangle$
\item Iteration 4: $from^3 = \langle S, x\rangle, to^4 = \langle T+1, x\rangle, new = \langle1\rangle$
\end{itemize}
The final reachable states are represented by multivariate polynomial ideal $\langle T^3\cdot x+x, T^4+T, x^2+x\rangle$,
which denotes $\{00,01,10,11\}$.
\end{Example}

\subsection{Use F-4 and ZDDs to Accelerate Polynomial Reduction}
In Chapter \ref{ch:reacha} and Chapter \ref{ch:normal}, by using RATO we transform the GB 
computation to a multivariate polynomial division. However, this division (reduction)
is still with exponential complexity at worst case. In a situation where 
a chain of OR gate exists, the size of polynomial will explode. For example, a chain of OR gates 
which can be written as Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
equals to following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice $f$ contains $2^4-1 = 15$ terms, which is exponential to number of variables.
The polynomial size explosion is a major factor affect the efficiency of polynomial division.

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=\textwidth]{newfig/red_steps}
}
\caption{The reduction process of chain of OR gates represent using ZDDs with order $d>c>b>a$}
\label{fig:ZDD}
\end{figure}

From Figure \ref{fig:ZDD} we find the size of the ZDD on the right-most side representing 
Equation \ref{eqn:chainOR} is $2\times4 -1 = 7$, which is linear to the number of variables.
The reduction process using ZDDs can be executed as in \cite{polybori:2009}. The graphical illustration 
of reduction in ZDDs is also shown in Figure \ref{fig:ZDD}.

\subsection{Interpolation extraction using GB Algorithm}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulae
\cite{pudlak:ci} \cite{mcmillan2003interpolation}. Assume that Boolean
formulae are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

\begin{Definition}
(From \cite{mcmillan2003interpolation}) Let $A$ and $B$ be Boolean
  formulae given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~iii)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

Given  the pair $(A, B)$ and their refutation proof, a procedure
called interpolation system constructs an interpolant in linear time
and space in the size of the proof \cite{mcmillan2003interpolation}
\cite{pudlak:ci}. 
\end{Definition}

@@

CIs are used to derive abstractions to produce over-approximate image
operators in model checking \cite{mcmillan2003interpolation}. Since $A
\implies P$, $P$ contains $A$ and is an {\it abstraction} of $A$. It
also has fewer variables, so checking  invariants on $P \wedge B$ is
easier. The interpolant is derived through a resolution proof of the
SAT problem. There can be many interpolants $P_i$ for a pair $(A,B)$; 
however, it is not feasible to explore a few or all of these
interpolants by means of the resolution proof.

{\bf Research problem 1:}
{\it As we wish to perform MC with abstraction using algebraic
  geometry, we introduce the algebraic geometry analog of CI
  and explore algorithms to compute them. We conjecture that the
  concept of CI should be related to elimination ideals, so our line
  of investigation will focus on \Grobner basis computations with
  elimination term orders for their computation.
}

@@

{\bf Research problem 2:}
{\it How can this algebraic interpolant $f_p$ (or in the general case,
  the set of polynomials $F_P$) be computed? As the interpolant $F_P$ 
contains only variables $X_C$ that are common to the polynomial sets
$F_A, F_B$, does this imply that the interpolants can be computed by
means of \Grobner bases with an elimination term order $X_A>X_B>X_C$
with $X_A, X_B$ eliminated from the problem? }

@@

{\bf Research problem 3:}
As there can be many interpolants for an ideal-pair $(J_A, J_B)$, we
will further resolve these questions:
\bi
\item Find the minimal interpolant: i.e. find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the un-eliminated
  variables. Consider Fig. \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: Projection of varieties on common variables? }
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional/macro blocks (including IP cores) and a raw netlist, 
technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as a alternative way to perform technology mapping, especially on word-level when 
given blocks represent word-level functions.

@@

Given a gate-level design $D$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $D$, and write out the mapped design $D'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $D$ with as many of $B_i$ such that the area
and timing is optimal. The procedure is also illustrated in Figure \ref{fig:macro}.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/macro.pdf}
	\end{center}
	\caption{The outline and flow of technology mapping of macro blocks}
	\label{fig:macro}
\end{figure}

@@

The following part describes the sketch of our proposed approach base on loop invariant constraints \cite{sankaranarayanan2004non}.
First, a transition system is modeled by algebraic assertions; then \emph{ideal membership test} \cite{lv:phd}
is applied on the set of assertions to help abstract the loop invariant. We introduce concept \emph{template}
from \cite{sankaranarayanan2004non} to apply on our proposed approach.

1) {\bf Template and state constraints:}  Ideal membership test technique requires a setup of ideal $J_{loop}$
for loop invariants. 
One heuristic can provide better coverage for loop invariant abstraction as well as
relatively small size is \emph{generic quadratic form} (GQF).

For example, the GQF of a pair of state variables $\{x,y\}$ is
$$\Func = a_0x^2+a_1x+a_2xy+a_3y+a_4y^2+a_5$$
It covers all possible terms with degree no more than 2. $a_0,a_1,\dots, a_5$ are usually real number parameters,
some of their assignments can turn $\Func$ into desired invariant. This parameterized constrain
polynomial covers all combinations of state variables can also be called a \emph{template}.
Subsequently, finding a proper assignment is the essential part of in our proposed research.

2) {\bf Initial state constraints:} For initial states, the constrains are explicit. A template is adopted and refined by Gr\"obner basis 
generated by original constrains, by equaling the remainder to 0 we can get constrains on
parameters from the template.

An example is shown in the following 3-line algorithm multiplying two natural numbers. 
\begin{align}
\label{eqn:loopinv}
& {\bf integer}~~i,j,s~~{\bf where}(s=0 \land j=j_0) \nonumber\\
& l_0: {\bf while}~~(\cdots)~~{\bf do} \nonumber\\
& ~~~~ l_1:~(s,j)\gets(s+i,j-1) 
\end{align}

Its template is generic quadratic form of $\{s,i,j,j_0\}$, which is
\begin{align}
\Func = & a_0s^2+a_1s+a_2si+a_3sj+a_4sj_0\nonumber\\
&a_5i^2+a_6i+a_7ij+a_8ij_0+a_9j^2\nonumber\\
&a_{10}j+a_{11}jj_0+a_{12}j_0^2+a_{13}j_0+a_{14}\nonumber
\end{align}
with parameters $a_0,\dots,a_{14}$.

Constrains of initial state $s=0\land j=j_0$ can be interpreted to polynomials:
$$\{s, j-j_0\}$$
Since their leading terms are relatively prime, the polynomial set itself constitutes a Gr\"obner basis 
$$G=\{s, j-j_0\}$$ 
Therefore its ideal can be written as
$J=\langle s,j-j_0\rangle$.

In the next step, we reduce the template with the Gr\"obner basis $G$: $\Func \xrightarrow{G}_+ r$, the remainder equals to
$$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$$
Let it equal to 0, then each coefficient will generate a constraint. The solution to the system forms the candidate
assignment to generate loop invariants.
\begin{equation}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\nonumber
\end{equation}

3) {\bf Modeling state transitions:}
A typical state transition starts from the previous state (PS) and ends at next state (NS). 
Our proposed approach models the 2 states individually,
{i.e.} performs polynomial reduction separately and obtains remainder $r_1$ and $r_2$. 
Assume a constraint polynomial describing
the state transition is $r_t$, then we require that when invariant of PS holds and transition $PS \to NS$ stands,
invariant of NS should also be satisfied:
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ can be any polynomial in arbitrary rings. To make it practical solving the system, 
we limit $\lambda$ to the polynomial ring with only real numbers.

We take Equation \ref{eqn:loopinv} as the example (which refers to Example 10 in \cite{sankaranarayanan2004non}). 
PS is initial state we just characterized 
$$\Func = f(s,i,j,j_0)$$ 
and NS has exactly the same form of constraint:
$$\Func' = f(s',i',j',j_0')$$
Considering the transition relation, we substitute $s'$ with $s+i$ and replace $j'$
with $j-1$, $i'$ for $i$, $j_0'$ for $j_0$, respectively. 
The template for NS is polynomial $f'$ in Example 10 in \cite{sankaranarayanan2004non}.

We then perform reduction with the Gr\"obner basis generated from the transition relation modeling, 
and record its remainder $r_2$.
From equality $r_2 = \lambda r_1$, we get constraints for the parameters. Solve the system using 
similar algorithm to solve binate covering problems
which is also described in Section 4 as \emph{elimination by splitting} technique in \cite{sankaranarayanan2004non}. 
One branching result is:
\begin{align*}
&a_0,a_2,\dots, a_6, a_9,\dots,a_{14}=  0\\ 
&a_1=a_7=-a_8
\end{align*}
The reduced remainder is: 
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Thus the invariant of the program in Equation \ref{eqn:loopinv} is:
$$s = i(j_0- j)$$
We can verify the invariant by executing the program which calculates $i\times j_0$. 
Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Equation \ref{eqn:loopinv}.

{\bf Our proposed approach on technology mapping:}
Our approach borrows inspiration of templates in \cite{sankaranarayanan2004non}. However, we make an improvement
on the original approach:
instead of using template polynomial to describe the system, we add some templates into the ideal
of macro blocks which serve as technology mapping candidates. In this way we can cover all possibilities
of boundary cutting (circuit partition).
